\begin{questions}

\question{Let $\Gamma$ be the fundamental solution of the heat equation in one space dimension defined by (9.2). Let $b : \R_+ \to \R$ and $a : \R_+\to \R_+$ be continuous. Let $B(t) = \int_0^tb(s)ds$ and $A(t) = \int_0^ta(s)ds$. Assume $A(t) > 0$ for all $t > 0$. Define
\begin{align*}
\tilde{\Gamma}(t,x)=\Gamma(x+B(t),A(t)),\quad x\in\R,t>0.
\end{align*}

Show that 
\begin{align*}
\partial_t\tilde{\Gamma}(t,x)=b(t)\partial_x\tilde{\Gamma}(t,x)+a(t)\partial^2_x\tilde{\Gamma}(t,x)
\end{align*}
}
\begin{solution}
By simply applying chain rule we get
\begin{align*}
\partial_t\tilde{\Gamma}(t,x)=B'(t)\partial_x\tilde{\Gamma}(t,x)+A'(t)\partial_t\tilde{\Gamma}(t,x).
\end{align*}
By the Fundamental Theorem of Calculus, $A'(t)=a(t)$ and $B'(t)=b(t)$. Further, by (9.3), $\partial_t\tilde{\Gamma}(t,x)=\partial^2_x\tilde{\Gamma}(t,x)$. Hence,
\begin{align*}
\partial_t\tilde{\Gamma}(t,x)=b(t)\partial_x\tilde{\Gamma}(t,x)+a(t)\partial^2_x\tilde{\Gamma}(t,x).
\end{align*}
\end{solution}
\question{Show that
\begin{align*}
\int_{\R}\tilde{\Gamma}(t,x)dx=1,\quad \int_{\R}x\tilde{\Gamma}(t,x)dx=-B(t),
\end{align*}
and
\begin{align*}
\int_{\R}(x+B(t))^2\tilde{\Gamma}(t,x)dx=2A(t).
\end{align*}
}
\begin{solution}
Let's start with the first one. Consider a change of variables similar to the tone used in the notes, $x+B(t)=y(4t)^{1/2}$. Then,
\begin{align*}
\int_{\R}\tilde{\Gamma}(t,x)dx&=\int_{\R}\Gamma(x+B(t),A(t))dx\\
&=\int_{\R}\Gamma(y(4A(t))^{1/2},A(t))\cdot(4A(t))^{1/2}dy\\
&=\pi^{-1/2}\int_{\R}e^{-y^2}dy=1.
\end{align*}
For the next one, consider the change of variables $y=x+B(t)$, then
\begin{align*}
\int_{\R}x\tilde{\Gamma}(t,x)dx&=\int_{\R}(y-B(t))\Gamma(x+B(t),A(t))dx\\
&=\int_{\R}y(4\pi A(t))^{-1/2}e^{-y^2(4A(t))^{-1}}dy-\int_{\R}B(t)(4\pi A(t))^{-1/2}e^{-y^2(4A(t))^{-1}}dy\\
&=\left.-A(t)^{-1/2}\pi^{-1/2}e^{-y^2(4A(t))^{-1}}\right|_{-\infty}^{\infty}-B(t)\int_{\R}(4\pi A(t))^{-1/2}e^{-y^2(4A(t))^{-1}}dy\\
&=0-B(t)=-B(t),
\end{align*}
where we have used the first part of the proof for the second integral. For the last one, we use integration by parts,
\begin{align*}
\int_{\R}(x+B(t))^2\tilde{\Gamma}(t,x)dx&=\int_{\R}-\sqrt{\frac{A(t)}{\pi}}(x+B(t))\left(-(x+B(t))(2A(t))^{-1}e^{-(x+B(t))^2(4A(t))^{-1}}\right)dx\\
&=\left.-\sqrt{\frac{A(t)}{\pi}}(x+B(t))e^{-(x+B(t))^2(4A(t))^{-1}}\right|_{-\infty}^{\infty}+\sqrt{\frac{A(t)}{\pi}}\int_{\R}e^{-(x+B(t))^2(4A(t))^{-1}}dx\\
&=0+\sqrt{\frac{A(t)}{\pi}}(4\pi A(t))^{1/2}\int_{\R}(4\pi A(t))^{-1/2}e^{-(x+B(t))^2(4A(t))^{-1}}dx\\
&=\sqrt{\frac{A(t)}{\pi}}(4\pi A(t))^{1/2}\\
&=\sqrt{\frac{A(t)}{\pi}}(4\pi A(t))^{1/2}\\
&=2A(t),
\end{align*}
where we have used the first result again.
\end{solution}	

\end{questions}