\begin{questions}

\question{Consider the Cauchy problem
\begin{align*}
&\frac{\partial u}{\partial t}+\sin{(\omega t)}u\frac{\partial u}{\partial x}=0,\\
&u(x,0)=u_0(x).
\end{align*}
Assume that $u_0$ is continuously differentiable on $\R$ and $\sup_x\left|u'_0(x)\right|\leq M$ for some $M>0$.
\begin{enumerate}[label=(\alph*)]
\item Show that the solution exists for all $t\geq 0$ provided that $\omega$ is large enough.
\item What can be done if $\omega$ is not sufficiently large?
\end{enumerate}
}
\begin{solution}
We start the like in the previous problem, by proving that $\zeta_z>0$. Generally
\begin{align*}
\zeta(z,t)=z+\int_0^tb\left(s,u_0(z)e^{\gamma s}\right)ds,
\end{align*}
and
\begin{align*}
\zeta_z(z,t)=1+u'_0(z)\int_0^tb_u\left(s,u_0(z)e^{\gamma s}\right)e^{\gamma s}ds,
\end{align*}
In our problem $b(t,u)=\sin{(\omega t)}u$ and $\gamma=0$. Therefore,
\begin{align*}
\zeta(z,t)=z+u_0(z)\int_0^tsin{(\omega s)}ds
\end{align*}
which we can integrate and obtain
\begin{align*}
\zeta(z,t)=z+\frac{u_0(z)}{\omega}\left[1-\cos{(\omega t)}\right].
\end{align*}
Differentiating with respect to $z$ we easily obtain
\begin{align*}
\zeta_z(z,t)=1+\frac{u'_0(z)}{\omega}\left[1-\cos{(\omega t)}\right].
\end{align*}
Like in the previous problem we can find a lower bound
\begin{align*}
\zeta_z(z,t)&\geq1-\left|\frac{u'_0(z)}{\omega}\left[1-\cos{(\omega t)}\right]\right|\\
&=1-\frac{\left|u'_0(z)\right|}{\left|\omega\right|}\left[1-\cos{(\omega t)}\right]\\
&\geq1-\frac{M}{\left|\omega\right|}\left[1-\cos{(\omega t)}\right]\\
&\geq1-2\frac{M}{\left|\omega\right|}.
\end{align*}
Thus, if $|\omega|>2M$, $\zeta_z(z,t)>0$ for all $z\in\R$ and $t\in[0,T)=[0,\infty)$. To prove that $\zeta\rightarrow\pm\infty$ as $z\rightarrow\pm\infty$ we use the Mean Value Theorem,
\begin{align*}
\zeta_z(\hat{z},t)=\frac{\zeta(z,t)-\zeta(0,t)}{z-0},
\end{align*}
where $\zeta(0,t)$ is independent of $z$, $\hat{z}$ is some value between $0$ and $z$, and $\zeta_z(\hat{z},t)>0$ for $\omega>2M$ as we just proved. Rearranging terms we get
\begin{align*}
\zeta(z,t)=z\zeta_z(\hat{z},t)+\zeta(0,t).
\end{align*}
Now we study two cases:
\begin{itemize}
\item If $z>0$,
\begin{align*}
\zeta(z,t)&=z\zeta_z(\hat{z},t)-\zeta(0,t)\\
&>z(1-2M)-\zeta(0,t)\rightarrow\infty\text{ as } z\rightarrow\infty,
\end{align*}
since $1-2M>0$ and constant.
\item If $z<0$,
\begin{align*}
\zeta(z,t)&=z\zeta_z(\hat{z},t)-\zeta(0,t)\\
&<z(1-2M)-\zeta(0,t)\rightarrow -\infty\text{ as } z\rightarrow -\infty,
\end{align*}
\end{itemize}
since $1-2M>0$ and constant. 

Thus, if $|\omega|>2M$, $\zeta_z(z,t)>0$ and $\zeta\rightarrow\pm\infty$ as $z\rightarrow\pm\infty$ for all $z\in\R$ and $t\in[0,T)=[0,\infty)$. Therefore, by \textsl{Theorem 3.11}, the Cauchy problem has a unique solution $u$ on $\R\times[0,\infty)$.

For part $b)$, if we want our solution to exist, but $\omega$ is not sufficiently large, i.e., $\omega<2M$, we have restrict $T$. We retake
\begin{align*}
\zeta_z(z,t)&=1+u'_0(z)\int_0^tb_u\left(s,u_0(z)e^{\gamma s}\right)e^{\gamma s}ds\\
&=1+u'_0(z)\int_0^t\sin{(\omega s)}ds\\
&\geq 1-\left|u'_0(z)\int_0^t\sin{(\omega s)}ds\right|\\
&\geq 1-\left|u'_0(z)\right|\int_0^t\left|\sin{(\omega s)}\right|ds\\
&\geq 1-M\int_0^tds\\
&\geq 1-Mt,
\end{align*}
which, since we need $\zeta_z(z,t)$ to be strictly greater than zero, gives us
\begin{align*}
1-Mt>0,
\end{align*}
and we can obtain a condition for $t$,
\begin{align*}
t<\frac{1}{M}=T^*.
\end{align*}
Thus, if $\omega$ is not large enough, $\zeta_z(z,t)>0$ for all $z\in\R$ and $t\in[0,T^*)$. To prove that $\zeta\rightarrow\pm\infty$ as $z\rightarrow\pm\infty$ we use again the Mean Value Theorem. Like above,
\begin{align*}
\zeta(z,t)=z\zeta_z(\hat{z},t)+\zeta(0,t).
\end{align*}
Now we study two cases:
\begin{itemize}
\item If $z>0$,
\begin{align*}
\zeta(z,t)&=z\zeta_z(\hat{z},t)-\zeta(0,t)\\
&>z(1-Mt)-\zeta(0,t)\rightarrow\infty\text{ as } z\rightarrow\infty,
\end{align*}
since $1-Mt>0$ and constant.
\item If $z<0$,
\begin{align*}
\zeta(z,t)&=z\zeta_z(\hat{z},t)-\zeta(0,t)\\
&<z(1-Mt)-\zeta(0,t)\rightarrow -\infty\text{ as } z\rightarrow -\infty,
\end{align*}
\end{itemize}
since $1-Mt>0$ and constant. 

Thus, if $|\omega|<2M$, $\zeta_z(z,t)>0$ and $\zeta\rightarrow\pm\infty$ as $z\rightarrow\pm\infty$ for all $z\in\R$ and $t\in[0,T^*)$. Therefore, by \textsl{Theorem 3.11}, the Cauchy problem has a unique solution $u$ on $\R\times[0,T^*)$.
\end{solution}
\end{questions}