\begin{questions}
\question{
Let $u:[0,L]\times[0,T]\rightarrow\R$ be continuous a twice continuously differentiable. Let $F:[0,L]\times[0,T]\rightarrow\R$ be continuous. Assume that
\begin{align*}
(\partial_t-\partial^2_x)u&=F(x,t),~~~~~~~~x\in[0,L],~t\in[0,T],\\
\partial_xu(0,t)=0&=\partial_xu(L,t),~~~~~~t\in[0,T],\\
u(x,0)&=0,~~~~~~x\in[0,L].
\end{align*}
Derive a Fourier series representation of $u$.
}
\begin{solution}
Let $\tilde{G}$ be the "modified Green's function" from \textsl{Problem 3.5.3} and set
\begin{align*}
u(x,t)=\int_0^L\int_0^t\tilde{G}(x,y,t-s)F(y,s)dsdy.
\end{align*}
Interchanging integration and the series representation of $\tilde{G}$, we obtain the Fourier cosine representation of $u$,
\begin{align*}
u(x,t)&=\int_0^L\int_0^t\sum_{m=0}^{\infty}\tilde{G}_m(x,y,t-s)F(y,s)dsdy\\
&=\sum_{m=0}^{\infty}\int_0^L\int_0^t\tilde{G}_m(x,y,t-s)F(y,s)dsdy\\
&=\sum_{m=0}^{\infty}u_m(x,t),~~~~~~\lambda_m=m\frac{\pi}{L},
\end{align*}
where 
\begin{align*}
u_m(x,t)&=\int_0^L\int_0^t\tilde{G}_m(x,y,t-s)F(y,s)dsdy\\
&=\frac{2}{L}\cos(\lambda_mx)\int_0^L\int_0^t\cos(\lambda_my)e^{-a\lambda_m^2(t-s)}F(y,s)dsdy,~~~~~~m\geq 1,
\end{align*}
and
\begin{align*}
u_0(x,t)&=\frac{1}{L}\int_0^L\int_0^tF(y,s)dsdy.
\end{align*}
Let us define $\alpha(s)=\int_0^L\cos(\lambda_my)F(y,s)dy$ to make the process shorter, then we have that 
\begin{align*}
u_m(x,t)&=\frac{2}{L}\cos(\lambda_mx)\int_0^t\alpha(s)e^{-a\lambda_m^2(t-s)}ds,~~~~~~m\geq 1,
\end{align*} 
We now prove that $u$ satisfy the PDE by first inspecting the terms separately. First we calculate $\partial_tu_m$ using Leibniz rule,
\begin{align*}
\partial_tu_m(x,t)&=\frac{2}{L}\cos(\lambda_mx)\left[\alpha(t)+\int_0^t\alpha(s)\left(-a\lambda_m^2e^{-a\lambda_m^2(t-s)}\right)\right]ds\\
&=\frac{2}{L}\cos(\lambda_mx)\alpha(t)-a\lambda_m^2\frac{2}{L}\cos(\lambda_mx)\int_0^t\alpha(s)e^{-a\lambda_m^2(t-s)}ds\\
&=\frac{2}{L}\cos(\lambda_mx)\alpha(t)-a\lambda_m^2u_m(x,t).\\
\end{align*}
On the other hand,
\begin{align*}
\partial^2_xu_m(x,t)=-\lambda_m^2u_m(x,t).
\end{align*}
Then,
\begin{align*}
(\partial_t-a\partial_x^2)u_m&=\frac{2}{L}\cos(\lambda_mx)\alpha(t)-a\lambda_m^2u_m(x,t)+a\lambda_m^2u_m(x,t)\\
&=\frac{2}{L}\cos(\lambda_mx)\int_0^L\cos(\lambda_my)F(y,t)dy\\
&=\frac{2}{L}\int_0^L\cos(\lambda_my)F(y,t)dy\cos(\lambda_mx)=:F_m(x,t).
\end{align*}
For the case of $m=0$,
\begin{align*}
\partial_tu_0(x,t)=\partial_t\frac{1}{L}\int_0^L\int_0^tF(y,s)dsdy=\frac{1}{L}\int_0^LF(y,t)dy,
\end{align*}
\begin{align*}
\partial_x^2u_0(x,t)=0.
\end{align*}
Then,
\begin{align*}
(\partial_t-a\partial_x^2)u_0&=\frac{1}{L}\int_0^LF(y,t)dy=:F_0(x,t)
\end{align*}
Hence, we see that $u$ satisfies the PDE,
\begin{align*}
(\partial_t-a\partial_x^2)u(x,t)&=(\partial_t-a\partial_x^2)\sum_{m=0}^{\infty}u_m(x,t)\\
&=\sum_{m=0}^{\infty}(\partial_t-a\partial_x^2)u_m(x,t)\\
&=(\partial_t-a\partial_x^2)u_0(x,t)+\sum_{m=1}^{\infty}(\partial_t-a\partial_x^2)u_m(x,t)\\
&=F_0(x,t)+\sum_{m=1}^{\infty}F_m(x,t)
=F(x,t).
\end{align*}
To check that satisfies the boundary conditions it sufices to check that each term of the series satisfies them,
\begin{align*}
\partial_xu_m(x,t)=\lambda_m\frac{2}{L}\sin(\lambda_mx)\int_0^t\alpha(s)e^{-a\lambda_m^2(t-s)}ds
\end{align*}
with
\begin{align*}
\partial_xu_m(0,t)=0\partial_xu_m(L,t),
\end{align*}
since the sine cancels at the boundaries. Since $u_0(x,t)$ does not depend on $x$, the boundary conditions are trivially satisfied. Note that $u$ satisfies the initial conditions as well.
\end{solution}
\end{questions}